NSHRDLU:\thanks{Name is provisional, and stolen from Geoff Hinton.}\\Work in progress on the joint learning of parsing and semantic encoding

### 2015-10-24 writing/gist/model1_fig.tex
Small additions and minor fixes to the gist writeup
Gist update.

    \tikzstyle{label}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{word}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{comp}=[fill=green!40,text width=20mm,align=center,text height=2mm]
    \tikzstyle{input}=[line width=1pt,text width=20mm,align=center,text height=2mm]    
    \tikzstyle{sbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=13.3mm]
    \tikzstyle{bbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=6.5mm]
    \tikzstyle{focus1}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=2mm]
    \tikzstyle{focus2}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=5.5mm]

@@

    \node[comp] (1c) at  (\ox+0.5*\oxb,\sy-1.5*\dy) {composition};

@@

 \caption{\label{fig:model:0}The Model 0 network unrolled for two transitions on the input \word{the cat sat down}. The operations at the bottom of the figure`  are given as inputs to the models, as is the start state of the stack at $t=0$.}

@@

    \tikzstyle{label}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{word}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{tracker}=[fill=red!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{softmax}=[fill=blue!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{comp}=[fill=green!40,text width=20mm,align=center,text height=2mm]
    \tikzstyle{result}=[line width=1pt,draw=black,text width=15mm,align=center,text height=2mm]    
    \tikzstyle{sbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=13.3mm]
    \tikzstyle{bbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=6.5mm]
    \tikzstyle{focus1}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=2mm]
    \tikzstyle{focus2}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=5.5mm]

>>>>

    \tikzstyle{label}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{word}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{comp}=[fill=green!40,text width=20mm,align=center,text height=2mm]
    \tikzstyle{compoff}=[fill=green!10!black!10,text width=20mm,align=center,text height=2mm]
    \tikzstyle{input}=[line width=1pt,text width=20mm,align=center,text height=2mm]    
    \tikzstyle{sbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=13.3mm]
    \tikzstyle{bbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=6.5mm]
    \tikzstyle{focus1}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=2mm]
    \tikzstyle{focus2}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=5.5mm]

@@

    \node[compoff] (1c) at  (\ox+0.5*\oxb,\sy-1.5*\dy) {composition};

@@

 \caption{\label{fig:model:0}The Model 0 network unrolled for two transitions on the input \word{the cat sat down}. The operations at the bottom of the figure are given as inputs to the models, as is the start state of the stack at $t=0$.}

@@

    \tikzstyle{label}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{word}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{tracker}=[fill=red!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{softmax}=[fill=blue!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{comp}=[fill=green!40,text width=20mm,align=center,text height=2mm]
    \tikzstyle{compoff}=[fill=green!10!black!10,text width=20mm,align=center,text height=2mm]
    \tikzstyle{result}=[line width=1pt,draw=black,text width=15mm,align=center,text height=2mm]    
    \tikzstyle{sbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=13.3mm]
    \tikzstyle{bbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=6.5mm]
    \tikzstyle{focus1}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=2mm]
    \tikzstyle{focus2}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=5.5mm]
